### 2017-06-13 Docs/Thesis/docs/appendix/appendixB.tex
modification on the thesis text

@@

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-lan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-wan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-bigflows-pcap}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-lan-pcap}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{lan-diurnal-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-wan-pcap}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{wan-pcap} and its approximations}
\end{figure}

>>>>

The trace \textit{bigflows-pcap} has a much higher inter packet rate, and a smaller dispersion. Weibull is the model chosen by AIC/BIC, and it is the second best on correlation and self-similarity (Exponential(Me) and Cauchy are the best respectively). Exponential(Me) chooses as the second preferable, has the closest to the original mean and standard deviation. Comparing the plots of the CDF function, the Weibull seams to express well both small and larger values of inter packet times, while Exponential(Me) is preciser on the mean values, as we can see at figure ~\ref{fig:aproximation-originalbigflows-cdf}.

@@

\begin{figure}[ht!]
	\centering
	\label{fig:qq-bigFlows}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:qq-lan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:qq-wan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-bigflows}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-lan}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/lan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{lan-diurnal-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-wan}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apB/val/wan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{wan-pcap} and its approximations}
\end{figure}

### 2017-06-13 Docs/Thesis/docs/chapter2.tex
modification on the thesis text

@@

The validation methods used on sourcesOnOff are: 
\begin{itemize}
\item Visual comparison between On time and Off time of the original trace and the stochastic fitting;
\item QQplots\footnote{
QQplot is a visual method to compare sample data with a specific stochastic distribution. It orders the sample data values from the smallest to largest, then plots it against the expected value given by the probability distribution function. The data sample values appear along the y-axis and the expected values along the x-axis. The more linear, the more the data is likely to be expressed by this specific stochastic distribution.
}, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
\item Measurement of Autocorrelation\footnote{
The autocorrelation functions measures the correlation between data samples $y_{t}$ and $y_{t + k}$, where $k =0, ..., K$, and the data sample $\{y\}$  is generated by an stochastic process.

>>>>

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=0.6\textwidth]{figures/ch2/qqplot-tutorial}
	\caption{ How information about may be extracted from QQplots. Source: "How to interpret a QQ plot" [Online]. Available: \href{https://stats.stackexchange.com/questions/101274/how-to-interpret-a-qq-plot}{https://stats.stackexchange.com/questions/101274/how-to-interpret-a-qq-plot} [Accessed 09 June 2017]}
	\label{fig:qqplot-tutorial}
\end{figure*}

Another way to analyze scalling characteristics is through QQplots. QQplot is a visual method to compare sample data with a specific stochastic distribution. It orders the sample data values from the smallest to largest, then plots it against the expected value given by the probability distribution function. The data sample values appear along the y-axis and the expected values along the x-axis. The more linear, the more the data is likely to be expressed by this specific stochastic distribution.

Dependendin on the type of plot, some behavios of the empirical dataset, compared to the theoretical may be observed. In the figure ~\ref{fig:qqplot-tutorial} is presented a sumary.

@@

The validation methods used on sourcesOnOff are: 
\begin{itemize}
\item Visual comparison between On time and Off time of the original trace and the stochastic fitting;
\item QQplots, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
\item Measurement of Autocorrelation\footnote{
The autocorrelation functions measures the correlation between data samples $y_{t}$ and $y_{t + k}$, where $k =0, ..., K$, and the data sample $\{y\}$  is generated by an stochastic process.

### 2017-06-13 Docs/Thesis/docs/chapter3.tex
modification on the thesis text

\subsubsection{Packet-level Traffic Generation Operation}

%2nd-review
At the packet level, it must use the expanded class of the \texttt{DummyFlow}. In this level, the job of our tool is to configure the underlying engine, to send a file. Therefore it uses the \textit{getters} available, and the passed parameters, defined by the operation described in the previous session. The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic using our framework. A more complex configuration is possible, but it serves to illustrate the procedure. Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}. 
\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{c++}
void flowGenerate(const counter& flowId, const time_sec& onTime, const uint& npackets, const uint& nbytes,  const string& netInterface)
{
	char localhost[CHAR_BUFFER];
	string strCommand;
	char command[CHAR_BUFFER];
	uint i = 0;
	int rc = 0;
	getLocalIp("eth0", localhost);
	strCommand += " -t " + std::to_string(onTime); 
	strCommand += " -k " + std::to_string(nbytes / 1024);
	strCommand += " -a " + getHostIP();
	if (this->getTransportProtocol() == PROTOCOL__TCP)
		strCommand += " -T TCP -D ";
	else if (this->getTransportProtocol() == PROTOCOL__UDP)
		strCommand += " -T UDP ";
	else if (this->getTransportProtocol() == PROTOCOL__ICMP)
		strCommand += " -T ICMP ";
	for(;;i++)
	{	
		StochasticModelFit idtModel = this->getInterDepertureTimeModel(i);
		if(idtModel.modelName() == WEIBULL)
		{
			strCommand += " -W " + std::to_string(idtModel.param1()) + " " + std::to_string(idtModel.param2());
			break;
		}
		else if ( idtModel.modelName() == CONSTANT)
		{
			strCommand += " -C " + std::to_string(nbytes/(1024*onTime));
			break;
		}
	}
	strcpy(command, strCommand.c_str());
	rc = DITGsend(localhost, command); // it is not blocking
    usleep(onTime*10e6);
	if (rc != 0)
	{
		printf("\nDITGsend() return value was %d\n", rc);
		exit(EXIT_FAILURE);
	}
}
\end{minted}

@@

\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{bash}
# Operation as a sniffer over a Ethernet interface named <ether-interface> 
./simitar --sniffer -if <ether-interface> --out/-o <cdt-name>
# Operation as a client using the traffic generator D-ITG, using a list of destination hosts of a text file
./simitar --client ditg --in <cdt-xml-name> --dst-list-ip <ip-list-file> 
# Operation as a packet injector with uses the Libtins library to craft packets
./simitar --pkt-injection libtins --in <cdt-xml-name> 
# Operation as a server. just runs D-ITG in the server mode.
./simitar --server/-sv ditg

>>>>

\subsubsection{Flow Generation Programming}

%2nd-review
At the packet level, it must use the expanded class of the \texttt{DummyFlow}. In this level, the job of our tool is to configure the underlying engine, to send a file. Therefore it uses the \textit{getters} available, and the passed parameters, defined by the operation described in the previous session. The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic. We call this concept \textit{Flow Generation Programming} A more complex configuration is possible, but it serves to illustrate the procedure. Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}. 
\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{c++}
void flowGenerate(const counter& flowId, const time_sec& onTime, const uint& npackets, const uint& nbytes,  const string& netInterface)
{
	char localhost[CHAR_BUFFER];
	string strCommand;
	char command[CHAR_BUFFER];
	uint i = 0;
	int rc = 0;
	getLocalIp("eth0", localhost);
	strCommand += " -t " + std::to_string(onTime); 
	strCommand += " -k " + std::to_string(nbytes / 1024);
	strCommand += " -a " + getHostIP();
	if (this->getTransportProtocol() == PROTOCOL__TCP)
		strCommand += " -T TCP -D ";
	else if (this->getTransportProtocol() == PROTOCOL__UDP)
		strCommand += " -T UDP ";
	else if (this->getTransportProtocol() == PROTOCOL__ICMP)
		strCommand += " -T ICMP ";
	for(;;i++)
	{	
		StochasticModelFit idtModel = this->getInterDepertureTimeModel(i);
		if(idtModel.modelName() == WEIBULL)
		{
			strCommand += " -W " + std::to_string(idtModel.param1()) + " " + std::to_string(idtModel.param2());
			break;
		}
		else if ( idtModel.modelName() == CONSTANT)
		{
			strCommand += " -C " + std::to_string(nbytes/(1024*onTime));
			break;
		}
	}
	strcpy(command, strCommand.c_str());
	rc = DITGsend(localhost, command); // it is not blocking
    usleep(onTime*10e6);
	if (rc != 0)
	{
		printf("\nDITGsend() return value was %d\n", rc);
		exit(EXIT_FAILURE);
	}
}
\end{minted}

@@

\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{bash}
# Operation as a sniffer over a Ethernet interface named <ether-interface> 
./simitar --sniffer --if <ether-interface> --out <cdt-name>
# Operation as a client using the traffic generator D-ITG, using a list of destination hosts of a text file
./simitar --client ditg --in <cdt-xml-name> --dst-list-ip <ip-list-file> 
# Operation as a packet injector with uses the Libtins library to craft packets
./simitar --pkt-injection libtins --in <cdt-xml-name> 
# Operation as a server. just runs D-ITG in the server mode.
./simitar --server ditg
